\Large\bf FlexibleSUSY --- A spectrum generator generator for supersymmetric models

### 2014-11-14 doc/flexiblesusy-paper.tex
added goodsell dirac gaugino rges paper and added jack+jones paper and paper with them and martin etc explaining discrepancies.

All model parameters and their $\beta$-functions are contained in
the first and second derived classes.  The structure of the
$\beta$-functions of a general supersymmetric model
\cite{Jones:1974pg,Jones:1983vk,West:1984dg,Martin:1993yx,Yamada:1993ga,MV94,Fonseca:2011vn,Yam94,Sperling:2013eva,Sperling:2013xqa}
allows to split these parameters into two classes:
%
\begin{enumerate}
\item \emph{SUSY parameters:} gauge couplings, superpotential
  parameters and VEVs and
\item \emph{soft-breaking parameters} \cite{Girardello:1981wz}: soft
  linear scalar terms, soft bilinear scalar interactions, soft
  trilinear scalar interactions, soft gaugino mass terms and soft
  scalar squared masses.
\end{enumerate}
%
The $\beta$-functions of the SUSY parameters in general depend only on
the SUSY parameters and are independent of the soft-breaking
parameters.  However, the $\beta$-functions of the soft-breaking
parameters depend on all model parameters in general.
%
This property is reflected in the C++ code: The class
\code{<model>_susy_parameters} directly inherits from
\code{Beta_functions} and implements the $\beta$-functions of the SUSY
parameters.  The class of soft-breaking parameters
\code{<model>_soft_parameters} in turn inherits from
\code{<model>_susy_parameters} and implements the $\beta$-functions of
the soft-breaking parameters in terms of all model parameters.  The so
constructed class hierarchy allows to (i) use the RGE running of all
model parameters via the common \code{Beta_function} interface and to
(ii) run the SUSY parameters independently of the soft-breaking
parameters.

@@

@@

%\cite{Yam94}
\bibitem{Yam94} 
  Y.~Yamada,
  %``Two loop renormalization group equations for soft SUSY breaking scalar interactions: Supergraph method,''
  Phys.\ Rev.\ D {\bf 50}, 3537 (1994)
  [hep-ph/9401241].
  %%CITATION = HEP-PH/9401241;%%
  %225 citations counted in INSPIRE as of 24 Sep 2013

>>>>

All model parameters and their $\beta$-functions are contained in
the first and second derived classes.  The structure of the
$\beta$-functions of a general supersymmetric model
\cite{Jones:1974pg,Jones:1983vk,West:1984dg,Martin:1993yx,Yamada:1993ga,Jack:1994kd,Jack:1994rk,Yam94,MV94,Fonseca:2011vn,Goodsell:2012fm,Sperling:2013eva,Sperling:2013xqa}
allows to split these parameters into two classes:
%
\begin{enumerate}
\item \emph{SUSY parameters:} gauge couplings, superpotential
  parameters and VEVs and
\item \emph{soft-breaking parameters} \cite{Girardello:1981wz}: soft
  linear scalar terms, soft bilinear scalar interactions, soft
  trilinear scalar interactions, soft gaugino mass terms and soft
  scalar squared masses.
\end{enumerate}
%
The $\beta$-functions of the SUSY parameters in general depend only on
the SUSY parameters and are independent of the soft-breaking
parameters.  However, the $\beta$-functions of the soft-breaking
parameters depend on all model parameters in general.
%
This property is reflected in the C++ code: The class
\code{<model>_susy_parameters} directly inherits from
\code{Beta_functions} and implements the $\beta$-functions of the SUSY
parameters.  The class of soft-breaking parameters
\code{<model>_soft_parameters} in turn inherits from
\code{<model>_susy_parameters} and implements the $\beta$-functions of
the soft-breaking parameters in terms of all model parameters.  The so
constructed class hierarchy allows to (i) use the RGE running of all
model parameters via the common \code{Beta_function} interface and to
(ii) run the SUSY parameters independently of the soft-breaking
parameters.

@@

%\cite{Yam94}
\bibitem{Yam94} 
  Y.~Yamada,
  %``Two loop renormalization group equations for soft SUSY breaking scalar interactions: Supergraph method,''
  Phys.\ Rev.\ D {\bf 50}, 3537 (1994)
  [hep-ph/9401241].
  %%CITATION = HEP-PH/9401241;%%
  %225 citations counted in INSPIRE as of 24 Sep 2013
%\cite{}
\bibitem{Jack:1994kd} 
  I.~Jack and D.~R.~T.~Jones,
  %``Soft supersymmetry breaking and finiteness,''
  Phys.\ Lett.\ B {\bf 333}, 372 (1994)
  [hep-ph/9405233].
  %%CITATION = HEP-PH/9405233;%%
  %195 citations counted in INSPIRE as of 14 Nov 2014

%\cite{Jack:1994rk}
\bibitem{Jack:1994rk} 
  I.~Jack, D.~R.~T.~Jones, S.~P.~Martin, M.~T.~Vaughn and Y.~Yamada,
  %``Decoupling of the epsilon scalar mass in softly broken supersymmetry,''
  Phys.\ Rev.\ D {\bf 50}, 5481 (1994)
  [hep-ph/9407291].
  %%CITATION = HEP-PH/9407291;%%
  %170 citations counted in INSPIRE as of 14 Nov 2014

@@

%\cite{Goodsell:2012fm}
\bibitem{Goodsell:2012fm} 
  M.~D.~Goodsell,
  %``Two-loop RGEs with Dirac gaugino masses,''
  JHEP {\bf 1301}, 066 (2013)
  [arXiv:1206.6697 [hep-ph]].
  %%CITATION = ARXIV:1206.6697;%%
  %23 citations counted in INSPIRE as of 14 Nov 2014
